Fractional Types

### 2019-11-22 fracGC/p.tex
minor

To make the space usage explicit in every step of evaluation, we
define an abstract machine whose states are pairs of a code register
and a memory register. In a low-level implementation the code register
would contain a pointer to the current instruction and the memory
register would contain a bit-level runtime representation of values
with one bit for boolean values, etc. In the Agda formalization, we
include the current combinator in the code register, and represent the
memory register using an index into an enumeration. Thus a memory
register containing a boolean value would be represented in Agda as 𝔽
::  𝕋 :: [] [ Fin.0F ] or 𝔽 :: 𝕋 :: [] [ Fin.1F ] depending on whether the
values is \AgdaInductiveConstructor{false} or \AgdaInductiveConstructor{true}.
The prepended list
contains all possible values of the type and the number in between [\ldots ]
is an index into the list, representing a finite number that
is guaranteed to be in bounds. In a low-level runtime representation
only a binary encoding of this finite type would need to be stored, but in
order to just prove that space is preserved, we can just inspect the
size of the prepended list. Putting it all together, machine states and
small-step reductions are formalized as follows:

@@

\begin{figure}[htb]
\includegraphics[scale=0.5]{trace2.png}
\caption{Execution trace of \AgdaFunction{id'}}
\label{fig:trace-id}
\end{figure}

>>>>

To make the space usage explicit in every step of evaluation, we
define an abstract machine whose states are pairs of a code register
and a memory register. In a low-level implementation the code register
would contain a pointer to the current instruction and the memory
register would contain a bit-level runtime representation of values
with one bit for boolean values, etc. In the Agda formalization, we
include the current combinator in the code register, and represent the
memory register using an index into an enumeration. Thus a memory
register containing a boolean value would be represented as
\AgdaFunction{[𝔽 ,  𝕋 ][0]} or \AgdaFunction{[𝔽 ,  𝕋 ][1]} depending on whether the
values is \AgdaInductiveConstructor{false} or \AgdaInductiveConstructor{true}.
The prepended vector
contains all possible values of the type and the number in between [\ldots ]
is an index into the vector, representing a finite number that
is guaranteed to be in bounds. In a low-level runtime representation
only a binary encoding of this finite type would need to be stored, but in
order to just prove that space is preserved, we can just inspect the
size of the prepended list. Putting it all together, machine states and
small-step reductions are formalized as follows:

@@

\begin{figure}[htb]
\includegraphics[scale=0.4]{trace2.png}
\caption{Execution trace of \AgdaFunction{id'}}
\label{fig:trace-id}
\end{figure}
